Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber}}

### 2018-02-25 Paper.tex

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{40s: Block Information}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0x40 & \linkdest{blockhash}{}{\small BLOCKHASH} & 1 & 1 & Get the hash of one of the 256 most recent complete blocks. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv P(I_{\mathbf{H}_{\mathrm{p}}}, \boldsymbol{\mu}_{\mathbf{s}}[0], 0)$ \\
&&&& where $P$ is the hash of a block of a particular number, up to a maximum age.\\
&&&& 0 is left on the stack if the looked for block number is greater than the current block number \\
&&&& or more than 256 blocks behind the current block. \\
&&&& $P(h, n, a) \equiv \begin{cases} 0 & \text{if} \quad n > H_{\mathrm{i}} \vee a = 256 \vee h = 0 \\ h & \text{if} \quad n = H_{\mathrm{i}} \\ P(H_{\mathrm{p}}, n, a + 1) & \text{otherwise} \end{cases}$ \\
&&&& and we assert the header $H$ can be determined as its hash is the parent hash \\
&&&& in the block following it. \\
\midrule
0x41 & {\small COINBASE} & 0 & 1 & Get the block's beneficiary address. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv {I_{H}}_{\mathrm{c}}$ \\
\midrule
0x42 & {\small TIMESTAMP} & 0 & 1 & Get the block's timestamp. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv {I_{H}}_{\mathrm{s}}$ \\
\midrule
0x43 & {\small NUMBER} & 0 & 1 & Get the block's number. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv {I_{H}}_{\mathrm{i}}$ \\
\midrule
0x44 & {\small DIFFICULTY} & 0 & 1 & Get the block's difficulty. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv {I_{H}}_{\mathrm{d}}$ \\
\midrule
0x45 & {\small GASLIMIT} & 0 & 1 & Get the block's gas limit. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv {I_{H}}_{\mathrm{l}}$ \\
\bottomrule
\end{tabular*}

>>>>

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{40s: Block Information}} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0x40 & \linkdest{blockhash}{}{\small BLOCKHASH} & 1 & 1 & Get the hash of one of the 256 most recent complete blocks. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv P(I_{\mathbf{H}_{\mathrm{p}}}, \boldsymbol{\mu}_{\mathbf{s}}[0], 0)$ \\
&&&& where $P$ is the hash of a block of a particular number, up to a maximum age.\\
&&&& 0 is left on the stack if the looked for block number is greater than the current block number \\
&&&& or more than 256 blocks behind the current block. \\
&&&& $P(h, n, a) \equiv \begin{cases} 0 & \text{if} \quad n > H(h)_{\mathrm{i}} \vee a = 256 \vee h = 0 \\ h & \text{if} \quad n = H(h)_{\mathrm{i}} \\ P(H(h)_{\mathrm{p}}, n, a + 1) & \text{otherwise} \end{cases}$ \\
&&&& and we assert the header $H(h)$ can be determined from its hash~$h$ unless $h$ is zero. \\
\midrule
0x41 & {\small COINBASE} & 0 & 1 & Get the block's beneficiary address. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv {I_{H}}_{\mathrm{c}}$ \\
\midrule
0x42 & {\small TIMESTAMP} & 0 & 1 & Get the block's timestamp. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv {I_{H}}_{\mathrm{s}}$ \\
\midrule
0x43 & {\small NUMBER} & 0 & 1 & Get the block's number. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv {I_{H}}_{\mathrm{i}}$ \\
\midrule
0x44 & {\small DIFFICULTY} & 0 & 1 & Get the block's difficulty. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv {I_{H}}_{\mathrm{d}}$ \\
\midrule
0x45 & {\small GASLIMIT} & 0 & 1 & Get the block's gas limit. \\
&&&& $\boldsymbol{\mu}'_{\mathbf{s}}[0] \equiv {I_{H}}_{\mathrm{l}}$ \\
\bottomrule
\end{tabular*}
